Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-02-14 3dpas_intro.tex
Do miracles happen?

The analytical space spanned by the three ``D''s of data-intensive, distributed,
and dynamic provides a common vocabulary and effective framework to analyze
applications and infrastructure alike.  Subjecting a range of otherwise distinct
applications to a common analytical framework provides an opportunity to search
for similarities across applications and understand core differences.  The
diverse % set of requirements to support
D3 scenarios points to the need for a careful understanding of D3
characteristics as well as sophisticated, extensible, and skillfully architected
infrastructure.  A common framework thus informs infrastructure scientists and
cyberinfrastructure experts where effort is likely to yield maximum returns.
The advantages of providing a common but extensible vocabulary that can be used
by the entire community, application end-users, developers and infrastructure
scientists alike, in an emerging field cannot be overstated. We believe that
such vocabulary and terminology has been missing from the practice of
distributed cyberinfrastructure in general, with negative consequences.

>>>>

The analytical space spanned by the three ``D''s of data-intensive, distributed,
and dynamic provides a common vocabulary and effective framework to analyze
applications and infrastructure alike.  Subjecting a range of otherwise distinct
applications to a common analytical framework provides an opportunity to search
for similarities across applications and understand core differences.  The
diverse D3 scenarios points to the need for a careful understanding of D3
characteristics as well as sophisticated, extensible, and skillfully architected
infrastructure.  A common framework thus informs infrastructure scientists and
cyberinfrastructure experts where effort is likely to yield maximum returns.
The advantages of providing a common but extensible vocabulary that can be used
by the entire community, application end-users, developers and infrastructure
scientists alike, in an emerging field cannot be overstated. We believe that
such vocabulary and terminology has been missing from the practice of
distributed cyberinfrastructure in general, with negative consequences.
